The imprint of global magma oceans on exoplanet demographics

### 2023-03-06 src/tex/ms.tex
edit false positives

\subsubsection{False positive scenarios}
\todo{what other processes could be confused with a magma ocean signal?\\
If there's no other subsubsection here, make this a (the final?) subsection in ``Discussion''.}
\begin{note}
    Global magma oceans are not the only physical mechanism that may cause a decrease in transit radii for a subset of planets.
    Other causes of shrinking planet sizes have been put forward, the most widely discussed ones being atmospheric loss due to either photoevaporation through high-energy radiation by the host star~\citep[e.g.,][]{Owen2013,Jin2014,Mordasini2020a} or due to residual heat from the planet's interior shortly after formation~\citep{Ginzburg2016b,Ginzburg2018,Gupta2019}.
    Both processes are being traded as potentially sculpting the observed radius bimodality of small, close-in exoplanets from the  mission~\citep{Fulton2017,VanEylen2018}.
    Like the magma ocean effect discussed here, these processes reduce the radii of some planets, leading to a decrease in average measured planet radii in a specific region of the planetary parameter space.
    This region is distinct from the one affected by global magma oceans, since... \todo{...elaborate why they cannot be confused}

>>>>

\subsubsection{False positive scenarios}
\todo{what other processes could be confused with a magma ocean signal?\\
If there's no other subsubsection here, make this a (the final?) subsection in ``Discussion''.}
\begin{note}
    Runaway greenhouse climates are not the only physical mechanism that may cause a change in transit radius for a subset of planets.
    Some of the most prominent alternative scenarios involve atmospheric loss due to either photoevaporation through high-energy radiation by the host star~\citep[e.g.,][]{Owen2013,Jin2014,Mordasini2020a} or due to residual heat from the planet's interior shortly after formation~\citep{Ginzburg2016b,Ginzburg2018,Gupta2019}.
    Both processes are being traded as potentially sculpting the observed bimodality in the radius distribution of small exoplanets~\citep{Fulton2017,VanEylen2018}.
%    Like the magma ocean effect discussed here, these processes reduce the radii of some planets, leading to a decrease in average measured planet radii in a specific region of the planetary parameter space.
    Either of them leads to a decrease of planet radius for planets close to their host star, which is distinct from the radius inflation introduced by runaway greenhouse climates.
